\begin{Requirements}
\section{Feature : Administrator}
Feature:  Administrator 
\subsection{Administrator WebUI Functional Requirement}

\subsubsection{FR-1  : Administrator log-in}
	  	-administrator enters credentials so system can validate them.
	 	-system grants access if administrator user-name and password is correct.
	 	-system denies if incorrect.
	  
\subsubsection{FR-2   : Administrator recover-password}
		-administrator has to select the recover-password option.
		-system send confirmation email to user-name email address.
		-administrator has to enter password sent to email.
	  	-system allows administrator to set a new password if confirmation email password was correct else reject and back to 			 log-in page.
\subsubsection{FR-3   :	Administrator granted access to system.}
  	
\subsubsection{FR-3.1 :	Administrator edits, update and delete records}
		-administrator has to select edit , update or delete records option.
		-administrator request user information from database.
		-system grants request and administrator can manipulate user's meta data.
		-users information should be updated in database when administrator is done editing.
		
\subsubsection{FR-3.2 :	Administrator block or unblock user.}
		-administrator has to select block or unblock option.
		-administrator requests users information from database.
		-system grants access to information.
		-administrator blocks or unblocks the user.
		-information has to be updated in the database.
		
\subsubsection{FR-3.3 :	Administrator adding new data capture-re or surveillance editor access to system.}
		-administrator has to select the add new data capture-re or surveillance editor option.
		-administrator must enter list of users permitted to access data-capturing or surveillance.
		-administrator must save the information on database and ensure the members on the list information is on the database 			 so system can grant them access.
		-system grants access to all the names on the list.
		
\subsubsection{FR-3.4 :	 Administrator deletes a data capture-re or surveillance.}
		-administrator has to select the delete data capture-re or surveillance editor option.
		-system fetches current list from database and displays it to administrator.
		-administrator selects and deletes name from list.
		-administrator has to also delete the information that is linked to that user name removed from the list.
\subsubsection{FR-3.5 :	Administrator view system performance}
		-Administrator should select the view system perfomance option.
\subsubsection{FR-3.6 : Administrator view data capture-re and surveillance editor changes.}
		-Administrator should select the view data capture-re and surveillance editor changes option.
		-Administrator should be able to view the data capture-re or surveillance editor of the website changes made.
•
\end{document}
		
	  	 
	  
