The agent is a metaphor for the system itself in a higher privilege right, such that it will have access to all the users' information and be able to analyse this, after which meaningful data will be generated from there and be used to form the real-time notifications that will be pushed to other users. The agent will be able to do the following:
\\
\bigskip

\FuncReq
{Analyse and integrate the information sent from user devices.}
{The agent will have access to different forms of data that the users will continuously send to it and the agent organises this data so that meaningful information can be extrapolated and used. This data will be in the form of location coordinates, stagnant users, step counters,user preferences and places of interest time taken on a specific route and possibly more. This data will then be analysed by the agent and real-time feedback will be given back to the users in terms of fastest routes, traffic congestion, places they may be interested in, nearby events, surveillance information and possibly more.}
{User will need administrative rights.}
{Trivial.}
    \\
    \textbf{Actor system interaction model: Analyse and integrate information sent from user devices. }\\
    \begin{tabular}{ | p{6cm} | p{6cm} |}
    \hline
    Actor: Mobile User & System: NavUp Agent\\ \hline
     0. The mobile user opens the application and has a view of the UP campus map & 1. The mobile application will display and indicate areas of high congestion, places of interest.\\ \hline
    
    \end{tabular}
\\
\bigskip


\FuncReq
{Privilege management and authentication.}
{The agent will be able to distinguish between the different types of users and convey the relevant information to them as well as differentiate the type of access rights that each type of user has on the data, for example mobile users will only have read access to congestion data, agents will have read and write data and administrators will have read and write access on the data.}
{User will need administrative rights.}
{Trivial}
    \\
    \textbf{Actor system interaction model: Privilege management and authentication.}\\
    \begin{tabular}{ | p{6cm} | p{6cm} |}
    \hline
    Actor: Mobile User & System: NavUp Agent\\ \hline
    & 0. The agent sets the read and write access on the system.\\ \hline
    1. The user logs in to the system &\\ \hline
    & 2. The system allows certain access depending on the type of user.\\ \hline
    \end{tabular}
\\
\bigskip