The data-capture adds the system's metadata such as building location , history ,campus events etc.
Since the system will provide indoor navigation the metadata inside the will not be entirely visible on the external map hence on entrance of a building the map needs to change to display a map of the building entered.

\FuncReq{ Data-capture user log-in}
	  	{-Administrator enters credentials so system can validate them.
	 	-System grants access if administrator user-name and password is correct.
	 	-System denies if incorrect.}
                  {TODO}
                  {TODO}
\FuncReq{ Data-capture user recover-password}
		{-Administrator has to select the recover-password option.
		-System send confirmation email to user-name email address.
		-Data-capture user has to enter password sent to email.
	  	-System allows data-capture user to set a new password if confirmation email password was correct else reject and back                    to log-in page.}
                {TODO}
                {TODO}               
\subsubsection {External map  metadata }
\FuncReq { 
\FuncReq {Adding or updating the campus building names on the system}
         {-Data-capture may add or update a building names that are locations on the map.
          -System displays the map of the campus and data-capture user may select a location and add or update the building name.}
          {TODO}
          {TODO}
\FuncReq{Adding or updating a buildings history}
         {-Data-capture user may add or update a building's history that is on the map.
          -System displays the map of the campus and data-capture user may select a existing building and add or update the                         building's history.}
          {TODO}
          {TODO}
\FuncReq{Adding or updating a buildings or area as a point of interest}
         {-Data-capture user may add a building or an area as a point of interest.}
          -System displays the map of the campus and data-capture user may select a existing building or area and add it as a                      point of interest.}
          {TODO}
          {TODO}
\FuncReq{Adding or updating an event}
        {-Data capture user may add a event or update so it is displayed on the map.
        -System displays the map of the campus and data-capture user may select a existing building , lecture hall , room or area and            add or update event so that the location or area is highlighted to display event taking place. A read further option is                  available for more details of the event.Data-capture user has to supply the details when adding the event.}
        {TODO}
        {TODO}
\FuncReq {Labeling a entrance.}
         {-Data-capture user may add or update the name of a entrance of the campus.}
         {-System displays the map of the campus and data-capture user may select a existing entrance on the map and label the entrance.
         Information will be updated on the map.}
         {TODO}
         {TODO}
\subsubsection { Internal map metadata }
\FuncReq {Adding or updating the locations inside a building on the system}
         {-Data-capture user may add or update lecture halls ,rest rooms or office names that are locations on the map.
          -System displays the map of the campus and data-capture user may select a location and add or update the name of the                      location.}
          {TODO}
          {TODO}
\FuncReq{Adding a elavator or stair cases inside a building on the system}
         {-Data-capture user may label an existing elavators, stair case, emergency exit location inside a building on the system.
         {-System displays internal map and the data capture user may select the elevator or stair case then label it so it can be                  highlighted on the map.}
         {TODO}
         {TODO}
 

 
         
           
         
