The Web User Interface will be used by system administrators to manage the system, as such the Web UI for goals and activities will be managed on this interface.

\FuncReq
{Add and create activities for the goals.}
{The system shall provide an interface for an admin user to add and create goals for the users to aim to achieve. The admin must be able to set what the requirements to reach the goals are, and the time frame allocated for achieving these goals, such as daily or weekly. The admin will also be able to see which users have met the goals that have been set. This data should be able  to be sorted by time taken to reach the goal or by who achieved the highest score in order to decide on who can win a prize.}
{Preconditions}
{Postconditions}

\FuncReq
{The system shall provide means to add prizes.}
{The system shall provide a way to add prizes that may be won by users as an incentive for completing goals. Each goal will be able to have a prize associated with it so that the user may see what they are eligible to win for completing the goal. Harder goals to achieve can then have better prizes associated with them to add to the incentive. The system shall display users who have achieved a goal and are eligible to win a prize. The choosing of a winner for a goal is at the discretion of the admin. Contact options for user who have completed the goal will be available to the admin in order to inform them of their prize.}
{The system will provide a means to save a list of available prizes so that they may be allocated. Goals must also be in place in order to assign prizes to them.}
{Postconditions}
