One of the concerns raised by the developing team was the issue of the life time of the system/mobile application. Students might not see the benifit of the mobile apllication seeing that the majority of students know the layout of campus and where venues are located. The client mentioned incentive in the form of a Goal and Reward System. The client did not expand on this issue so this might be subject to change. Here are a few requirements if such a system was implemented in NavUP:

\FuncReq
{Track the user's steps or distance walked.}
{The mobile application will have to keep track of the users steps or measure the distance they have walked. This data will be saved and used when tracking the goals and achievements of the user. It will also be visible to the user for them to see how much/far they have walked.}
{TODO}
{TODO}

\FuncReq
{Display the various fun run routes on campus.}
{Campus has varius fun run routes marked by painted animal footprints. These footprints have in time faded away, therefore it will be benefitial to display these routes to the user when they want to reach a certain goal or even just have a jog for exercise. This can be displayed on the map as a navigational route.}
{TODO}
{TODO}

\FuncReq
{Set goals for the user to finish.}
{The client has not expanded on this section, therefore there can only be assumed that the mobile app will have certain goals/achievements listed. This will most likely be in the form of a certain distance walked or a number of steps taken. These goals will have to be set by the administrators and will have various levels of completion, each level awarding a prize to the user.}
{TODO}
{TODO}

\FuncReq
{Notify the user when they have reached/completed a goal.}
{The mobile app will have to notify the user when they have reached a certain goal or even a user's personal goal. This will allow the user to move to the next goal. This can be done via push notifications. The goals can also be tracked by the user to see how far they are from completing it.}
{TODO}
{TODO}

\FuncReq
{Display the user's statistics for review.}
{The mobile app will need a statistics section where the overall progress and steps taken/distance traveled will be recorded and displayed. This may include maximum distance walked in a day to average step count depending on the clients final wishes on this section.}
{TODO}
{TODO}

\FuncReq
{Notify the user when they have been awarded a prize.}
{The mobile app will also need to notify the user when they have been awarded a prize. These prizes will be the responsibility of the client and it is up to them to set when such a prize is rewarded. The notification will then display a message of what the user has won.}
{TODO}
{TODO}

\FuncReq
{Display information/guide of how users can collect their prizes.}
{The client will have to provide the information needed to collect a prize and where to do so. This information will then be displayed to the user along with contact details if anything is uncertain. Again this is up to the client and how they want to implement this section, for now only assumptions can be made.}
{TODO}
{TODO}