In regards to the Guest Users, they will have the same requirements of a Base User (See Base User Requirements). They won't have an associative ID linking them to the database seeing as they will not be logged in. As soon as they do so they will be seen as a Logged In User. The only possible added functionality will be catering to people who don't visit campus often. See below mentioned for expanded requirements:
\bigskip
\\    

\FuncReq
{A better view of points of interest on the map.}
{A guest user will most likely be someone visiting campus. It will thus be beneficial to the user if the points of interest are more visible to them. This will allow them to easily find any usefull information they might need. This can be done by highlighting or setting points on the map itself for the user to select and read further information on that point.}
{Trivial}
{Trivial}
\\
\textbf{Actor system interaction model: A better view of points of interest on the map.}\\
\begin{tabular}{ | p{6cm} | p{6cm} |}
\hline
Actor: Mobile Guest User & System: NavUp \\ \hline
& 0. The mobile app displays a map of the campus.\\ \hline
1. The user selects a destination & 2. The mobile application will display in a more visual way various points of interest along the path to the destination.\\ \hline
\end{tabular}
\\
\bigskip
\\    
\textbf{Actor system interaction model: A better view of points of interest on the map. }\\
\begin{tabular}{ | p{6cm} | p{6cm} |}
\hline
Actor: Mobile Guest User & System: NavUp \\ \hline
& 0. The mobile app displays a map of the campus.\\ \hline
1. The user selects a location on the map & 2. The mobile application will display in a more visual way various points of interest in the surrounding areas.\\ \hline
\end{tabular}
\\
\bigskip

\FuncReq
{A better view of activities/events happening on campus.}
{Campus plays host to various events and activities like Business days or even music orchestras. This means that campus will have a number of guests unfamiliar with the layout of campus or the location of these activities/events. The guest user needs to be able to view the activities/events in a more visible way. This will allow them to navigate to their destination and/or read more information on it. This can also be displayed on the map or even on a sub-menu for ease of access.}
{Trivial}
{Trivial}
\\
\textbf{Actor system interaction model: A better view of activities/events happening on campus.}\\
\begin{tabular}{ | p{6cm} | p{6cm} |}
\hline
Actor: Mobile Guest User & System: NavUp \\ \hline
& 0. The mobile app displays a map of the campus.\\ \hline
1. The user selects a destination & 2. The mobile application will display in a more visual way various events and activities along the path to the destination.\\ \hline
\end{tabular}
\\
\bigskip
\\    
\textbf{Actor system interaction model: A better view of activities/events happening on campus. }\\
\begin{tabular}{ | p{6cm} | p{6cm} |}
\hline
Actor: Mobile Guest User & System: NavUp \\ \hline
& 0. The mobile app displays a map of the campus.\\ \hline
1. The user selects a location on the map & 2. The mobile application will display in a more visual way various events and activities happening in the surrounding areas.\\ \hline
\end{tabular}
\\
\bigskip

