\begin{Requirements}
\section{Feature : Surveillance}
Feature:  Surveillance 
\subsection{Surveillance functional requirements}
 \FuncReq{Surveillance log-in :}
 		{-Surveillance user needs to enter their user-name.
 		-Surveillance user needs to enter their password.
 		-System grants access if user-name and password are correct.}
 		 {TODO}
		 {TODO}
 \FuncReq{Surveillance recover-password}
 		{-System has to select the recover-password option.
 		-System send confirmation email to user-name email address.
		-Surveillance user has to enter password sent to email.
	  	-System allows surveillance user to set a new password if confirmation email password was correct 			 else reject and back to log-in page.}
	  	 {TODO}
		 {TODO}
\subsubsection{Surveillance user granted access to system}
\FuncReq{Surveillance user views heat-map}
		{-User has to select view option to view the current heat-map.}
		 {TODO}
		 {TODO}
\FuncReq{Surveillance user edits heat-map}
		{-User has to select edit heat-map option.
		\subsubsection{scenario:}
		 {User wants to change heat-map display colors.}
		{-Current colors of the heat-map are displayed.
		-Surveillance user selects option to change the heat-map color.
		-Surveillance user has to select the new colors from available options.
		-System is updated in the new color selected by surveillance user.}	
		}
		 {TODO}
		 {TODO}	
\FuncReq{Surveillance tracks a user's location}
		{-Surveillance user has to select track user option.
		-System requires user-name of the user that should be tracked.
		-System returns current location of user if user is connected.
		-Surveillance can view users current location and see distance traveled by user around the campus.}
		 {TODO}
		 {TODO}
\FuncReq{Surveillance analyze certain location and set peak times information}
		{-Surveillance user has to select the peak times option.
		-Surveillance user submits a request to compare system user location times.
		-Surveillance user sets peak times information.
		-Surveillance user submits peak times to database.}
		 {TODO}
		 {TODO}
\FuncReq{Setting prizes to be awarded to the system users}
		{-Surveillance user has option to view statistical data of the users to select the winner for a specific prize.
		 -Surveillance can set a prize for the winner.}
		 {TODO}
		 {TODO}
		  	
